\documentclass[../report.pdf]{subfiles}
\begin{document}
During the course of the project, the main challenge faced by the team was a lack of knowledge of Bluetooth Low Energy technology, Firebase, or Android app development. To rectify this issue, we set up a Discord server that allowed us to meet almost everyday to pool our resources, videos, knowledge, and data on how to do every part of the app. We learnt on a weekly basis about Android App Lifecycle, Firebase Authentication, Firebase Database, and Bluetooth Gatt roles through official documentation, articles, and tutorial videos. We also learnt about Android Studio and how to use GitHub to add our code to branches for version control. We learned how to make UI designs using HTML, CSS, VUe.js and how to add open source libraries to aid us in our work. We learnt how to use emulators to test a bunch of our code, and how to use real phones to test our Bluetooth functionalities since they don’t work on emulators. We met weekly, learnt everything we could and taught ourselves everything we didn't know through the use of our Discord server and through official Teams meetings. We are proud to say that we have logged a total of 17 formal meetings alone and was ahead of schedule for most of the project.

We researched and took heavy inspiration from the existing app Instatt, but revamped it with brand new attendance taking technology, as well as a minimalist, high contrast aesthetic. Previous topics covered in our modules such as Java, SQL, HTML and CSS helped us code this complex application. During this period we also faced a myriad of other assignments and exams due at the same time. We developed this app with our blood and sweat, while losing hours and days of sleep at a time. 

During our testing phase of the app, we discovered that we could not use emulators to emulate Bluetooth Functionalities. Thus, we came to a solution to use the only three Android phones one of us had to test our application. The software demonstration videos are screen recordings of real phones using the app due to the ongoing pandemic. Most of the tests passed; Those that failed were likely due to a device related issue. Thus, our app is fully functional on functioning devices.

As of right now, the app does not work on iOS devices, and has not been integrated into the UNMC database. However, we have implemented a Firebase Firebase and a working Bluetooth Low Energy app that takes attendance automatically in the background using the waterfall model, which took a lot of hard work from all of us. 

All in all, we can safely say that the completion of our whole project was handled step by step systematically. At the end of the day, what we accomplished was a fully operational system with real time updates, that after final bug checks, will be ready for version 1.0 rollout.
\end{document}